---
title: "Social Survey"
author: "Put your name here!"
date: "put the date here"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS2016_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->



<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   

####This study deals with questions about possible relationships between views toward extramrital sex and sex, political views, and current relationship status. The data is from the 2016 general social survey.



# Sex

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
```{r}
source("makeTables2016.R")
barchartGC(xsex_sex,type="percent")
```

In the bar chart you can see that women aren't thrilled on the idea of nonmarital sex. One one side women are about 55 percent against it while males are about 40 percent against it. The next bar you see men not really being against or for the idea of nonmarital sex and women have a lower chance of being indifferent. The next bar women and men are about the same average of being okay with nonmarital sex.

```{r}
chisqtestGC(xsex_sex,graph= TRUE)

```

The p value is .0351. If the null hypothesis is true you get the result of this 3 percent of the time. The males and females opinion about non marital sex seems the same this is why we reject the null hypothesis.



# Polyviews

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Relationship status




```{r}
chisqtestGC(xmsex_table,graph= TRUE)

```
The p value is 
0.006. If the null hypothesis is true you get the result of this 3 percent of the time. The hooked up and single people opinion about non marital sex seems the same this is why we reject the null hypothesis.
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
