---
title: "Social Survey"
author: "Put your name here!"
date: "put the date here"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS2016_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->



<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   

####This study deals with questions about possible relationships between views toward extramrital sex and sex, political views, and current relationship status. The data is from the 2016 general social survey.



# Sex

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->


# Polyviews

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Relationship status

```{r}
source("makeTables2016.R")
barchartGC(xmsex_table,type="percent")
```
In the bar chart you can see that people that hooked up are seeing the wrong aspect as about 80%, the hmmm reaction as 80% and are out about it about 60%. 15% of people think it's wrong, about 20% think it's a maybe yes or maybe no, and more than 20% believe it is okay to hook up.This means that people who have hooked up are more open to the idea of relationship status of premartial sex while mostly all singles believe it's not okay.




```{r}
chisqtestGC(xmsex_table,graph= TRUE)

```
The p value is 
0.006. If the null hypothesis is true you get the result of this 3 percent of the time. The hooked up and single people opinion about non marital sex seems the same this is why we reject the null hypothesis.
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
