---
title: "Social Survey"
author: "Put your name here!"
date: "put the date here"
output:
  html_document: default
---

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
source("Import_GSS2016_haven.R")
```
<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->   

####This study deals with questions about possible relationships between views toward extramrital sex and sex, political views, and current relationship status. The data is from the 2016 general social survey.



# Sex

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
```{r}
source("makeTables2016.R")
barchartGC(xsex_sex,type="percent")
```

In the bar chart you can see that women aren't thrilled on the idea of nonmarital sex. One one side women are about 55 percent against it while males are about 40 percent against it. The next bar you see men not really being against or for the idea of nonmarital sex and women have a lower chance of being indifferent. The next bar women and men are about the same average of being okay with nonmarital sex.

```{r}
chisqtestGC(xsex_sex,graph= TRUE)

```

The p value is .0351. If the null hypothesis is true you get the result of this 3 percent of the time. The males and females opinion about non marital sex seems the same this is why we reject the null hypothesis.

#Ployviews

```{r}
source("makeTables2016.R")
barchartGC(xsex_polv,type="percent")

```

In the bar chart it shows that the liberals find extramarital sex 25 percent wrong, People who are moderate feel it's 39 percent wrong, and Conservatives feel it's 46 percent wrong. Liberals feel indifferent more than 50 percent, People who are moderate feel it's 45 percent indifferent. The conservatives feel it's indifferent is 15 percent. 45 percent of liberals feel it is 15 percent okay, People who are moderate are 35 percent of them believe it's okay, and Conservatives who are 20 percent of them are okay bout extramarital sex.

```{r}
chisqtestGC(xsex_polv,graph= TRUE)

```

The p value is .0351. If the null hypothesis is true you get the result of this 3 percent of the time. The males and females opinion about non marital sex seems the same this is why we reject the null hypothesis. A small p-value (typically ≤ 0.05) indicates strong evidence against the null hypothesis, so we reject the null hypothesis.



## Relationship status

```{r}
source("makeTables2016.R")
barchartGC(xmsex_table,type="percent")
```
In the bar chart you can see that people that hooked up are seeing the wrong aspect as about 80%, the hmmm reaction as 80% and are out about it about 60%. 15% of people think it's wrong, about 20% think it's a maybe yes or maybe no, and more than 20% believe it is okay to hook up.This means that people who have hooked up are more open to the idea of relationship status of premartial sex while mostly all singles believe it's not okay.




```{r}
chisqtestGC(xmsex_table,graph= TRUE)

```
The p value is 
0.006. If the null hypothesis is true you get the result of this 3 percent of the time. The hooked up and single people opinion about non marital sex seems the same this is why we reject the null hypothesis.



# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!--> These test showed the differncces of each bar graph and the p value. This helped us recognize the ability to identify graphs and p values.
